|

### 2021-07-22 prova_knit_finale.Rmd
small change

In the previous chapter we explained how the Kalman Filter is applied to the case of a linear model with Gaussian errors to find closed-form solution for the filtering and the predictive distributions. Nonetheless, the majority of time-series models have a non-linear structure and errors might follow non-Gaussian distributions.\
In this chapter we describe \textit{particle filter} as an algorithm that allows to update sequentially the filtering and the predictive distributions in the non-linear and non-Gaussian case. Additionally, the Kalman Filter can be seen as a special case of the more general particle filter.\
In section \ref{pf_intro} we introduce the fundamental notions of \textit{importance sampling}, \textit{sequential importance sampling} and \textit{resampling}. Then, in section \ref{pf_main} we describe three particle filtering algorithms: the \textit{bootstrap}, the \textit{guided} and the {auxiliary particle filters}. Instead, in section \ref{pf_lui_west} we describe the {Liu and West filter}, when particle filtering is used to estimate model's parameters. Finally, in section \ref{pf_converg} we establish some general convergence results for Particle Filter - Monte Carlo estimators.

>>>>

In the previous chapter we explained how the Kalman Filter is applied to the case of a linear model with Gaussian errors to find closed-form solution for the filtering and the predictive distributions. Nonetheless, the majority of time-series models have a non-linear structure and errors might follow non-Gaussian distributions.\
In this chapter we describe \textit{particle filter} as an algorithm that allows to update sequentially the filtering and the predictive distributions in the non-linear and non-Gaussian case. Additionally, the Kalman Filter can be seen as a special case of the more general particle filter.\
In section \ref{pf_intro} we introduce the fundamental notions of \textit{importance sampling}, \textit{sequential importance sampling} and \textit{resampling}. Then, in section \ref{pf_main} we describe three particle filtering algorithms: the \textit{bootstrap}, the \textit{guided} and the \textit{auxiliary particle filters}. Instead, in section \ref{pf_lui_west} we describe the \textit{Liu and West filter}, when particle filtering is used to estimate model's parameters. Finally, in section \ref{pf_converg} we establish some general convergence results for Particle Filter - Monte Carlo estimators.
